FEM Transition Models

### 2023-03-13 FEM_R/Loneliness_Social_Isolation/PAPER_WORKING_SCRIPT.Rmd
Did some testing and improving the social isolation model, and fixed an error in the WORKING_SCRIPT where a dplyr function had been masked

# Need counts of non missing data per variable to calculate SD from SE
counts <- s %>% summarise_each(funs(sum(!is.na(.)))) %>%
  select(age, male, bmi, smoken, smokev, hsless, college) %>%
  t() %>%
  as.data.frame() %>%
  tibble::rownames_to_column('Variable') %>%
  rename(n = 'V1')

>>>>

# Need counts of non missing data per variable to calculate SD from SE
counts <- s %>% summarise_each(funs(sum(!is.na(.)))) %>%
  dplyr::select(age, male, bmi, smoken, smokev, hsless, college) %>%
  t() %>%
  as.data.frame() %>%
  tibble::rownames_to_column('Variable') %>%
  rename(n = 'V1')

### 2023-03-13 FEM_R/Loneliness_Social_Isolation/transition_models_testing.Rmd
Did some testing and improving the social isolation model, and fixed an error in the WORKING_SCRIPT where a dplyr function had been masked

```{r}
## TEST
form.lnly.test <- 'lnly ~ male + hsless + college + scale(l2age65l) + scale(l2age6574) + scale(l2age75p) + l2cohab + l2widowed + l2single + l2employed + l2inactive + l2physact + l2anyadl + l2anyiadl + l2srh5 + l2psyche + l2hhres + l2socyr + l2gcareinhh1w + childless + scale(l2logatotb)'
probit.lnly.test <- polr(formula = form.lnly.test,
                    data = trans,
                    Hess = TRUE,
                    na.action = na.omit)
print('Test model:')
summary(probit.lnly.test)
```

>>>>

```{r}
## TEST
form.lnly.test <- 'lnly ~ male + hsless + college + scale(l2age65l) + scale(l2age6574) + scale(l2age75p) + l2cohab + l2widowed + l2single + l2employed + l2inactive + l2physact + l2anyadl + l2anyiadl + l2srh5 + l2hhres + l2socyr + l2gcareinhh1w + childless + scale(l2logatotb) + l2cesd'
probit.lnly.test <- polr(formula = form.lnly.test,
                    data = trans,
                    Hess = TRUE,
                    na.action = na.omit)
print('Test model:')
summary(probit.lnly.test)
```

## Social Isolation

First recreate the minimal and current models before trying anything new.

```{r}
# Get a sample comparable to the sample used in FEM
trans.sociso <- trans %>%
  dplyr::select(idauniq, wave, died, sociso, male, white, hsless, college, l2age65l, l2age6574, l2age75p, atotb, l2employed, l2inactive, l2physact) %>%
  filter(wave > 1) %>%
  filter(died == 0)
trans.sociso.complete <- trans.sociso[complete.cases(trans.sociso),]

## MINIMAL
form.sociso.min <- 'sociso ~ male + scale(l2age65l) + scale(l2age6574) + scale(l2age75p)'
probit.sociso.min <- polr(formula = form.sociso.min,
                    data = trans.sociso,
                    Hess = TRUE,
                    na.action = na.omit)
# print('Minimal model:')
summary(probit.sociso.min)

## FULL
form.sociso <- 'sociso ~ male + white + hsless + college + scale(l2age65l) + scale(l2age6574) + scale(l2age75p) + scale(atotb) + l2employed + l2inactive + l2physact'
probit.sociso <- polr(formula = form.sociso,
                    data = trans.sociso,
                    Hess = TRUE,
                    na.action = na.omit)
print('Full model:')
summary(probit.sociso)
```

Now trying the predictors from the loneliness model minus some variables that would be too strongly correlated with the outcome (specifically socyr).

```{r}
## TEST
form.sociso.test <- 'sociso ~ male + hsless + college + scale(l2age65l) + scale(l2age6574) + scale(l2age75p) + l2cohab + l2widowed + l2single + l2physact + l2srh5 + l2hhres + l2gcareinhh1w + childless + scale(l2logatotb) + l2cesd + l2sight + l2hearing + l2ahown'
probit.sociso.test <- polr(formula = form.sociso.test,
                    data = trans,
                    Hess = TRUE,
                    na.action = na.omit)
print('Test model:')
summary(probit.sociso.test)
```
